---
title: "Group Project"
output: html_document
date: "2023-03-31"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Set up libraries
```{r}
library(igraph)
library(igraphdata)
library(tidyverse)
library(kableExtra)
library(dplyr)
library(scales)
```

## Load Data
```{r}
data.survey <- read.csv("data_edgelist.csv", header=TRUE, row.names = NULL)

datasurveynew <- data.survey %>%
  group_by(Motivation, Impact) %>% #group data by motivation and impact
  tally(sort=TRUE) %>% #to find the number of unique combinations of Motivation and Impact categories and find edge weights
  rename(weight=n) %>% 
  ungroup()

datasurveynew <- as.data.frame(datasurveynew)
datasurveynew <- graph_from_data_frame(datasurveynew)

# Number of variables as nodes and connections between variables as edges
summary(datasurveynew)
```


## Visualisation
```{r}
par(mar=c(0,0,0,0)+.25) # to reduce the margins 
set.seed(10) # to get the same network layout 
plot(datasurveynew, vertex.label.cex=0.8, vertex.label.color = "blue", vertex.size = 20, vertex.frame.color='white', edge.arrow.size=0.3, edge.width = E(datasurveynew)$weight, layout=layout_with_kk, rescale=TRUE)
```

## Degree Distribution
```{r}
in_degree <- degree(datasurveynew, mode = "in", normalized = TRUE)
out_degree <- degree(datasurveynew, mode = "out", normalized = FALSE)
rbind(in_degree,out_degree)
```

## Centrality Analysis
### Strength Centrality
```{r}
node_strength <- strength(datasurveynew, mode = "all") %>% sort(decreasing=TRUE)
node_strength
```

### Betweenness centrality of each node - finding mediators
```{r}
betweenness <- betweenness(datasurveynew,
            v = V(datasurveynew),
            normalized = T, 
            directed = T) %>%
            sort(decreasing=TRUE) %>% 
            round(4)
betweenness
```

## Clustering Analysis
### Global clustering coefficient
```{r}
global_cc <- transitivity(datasurveynew, type = "global", weights = "weight")
global_cc
#since global cc is 0, there is no clustering in the network. it may be because the network is small or very sparse
```

### Local clustering coefficient
```{r}
local_cc <- transitivity(datasurveynew, type = "local", weights = "weight")
rbind(V(datasurveynew)$name,local_cc)
#since local cc is 0, there is no clustering in the network. it may be because the network is small or very sparse
```

## Community Detection
### Random walker (Walktrap)
```{r}
data_walktrap <- cluster_walktrap(datasurveynew, weights = E(datasurveynew)$weight)

# Membership of nodes in each community (under data_edge, there are a lot of objects inside. we are only using the object 'membership' for this community detection method)
data_walktrap_membership <- data.frame(node = 1:gorder(datasurveynew), 
                                       community = data_walktrap$membership)

table(data_walktrap_membership$community)

# Modularity of the network 
modularity(data_walktrap) 
#since the modularity of the communities that were retrieved is very low, low quality of communities retrieved
```

### Visualization of Communities
```{r}
par(mar=c(0,0,0,0)+.1)
set.seed(8) 

V(datasurveynew)$community <- data_walktrap$membership # assign community membership as a node attribute 

plot(datasurveynew, vertex.label.cex=0.6, vertex.color=V(datasurveynew)$community, # automatically assign colors to communities
    vertex.size = 10, vertex.frame.color = 'white', 
     edge.arrow.size=0.1, edge.width = E(datasurveynew)$weight, layout=layout_with_kk, rescale=TRUE)
```

### Average betweenness centrality of nodes within communities
```{r}
# Get the nodes belonging to each community
community_nodes <- split(V(datasurveynew), data_walktrap_membership$community)

# Calculate the degree for each node within each community
community_strength <- lapply(community_nodes, function(x) strength(datasurveynew, x))

# Calculate the average degree for nodes within each community
average_strength <- sapply(community_strength, mean)

# Print the results
print(average_strength)
```

